---
title: "Simulation: Craps Simulation"
format: html
---

There need to answer the following three questions:

1.Which probability do you want to estimate?
2.What is the simulation result (in numbers and visuals)?
3.What is the simulation variability?

Probability to Estimate
Estimate the probability of winning a single craps game. Specifically, we want to determine:

What is the likelihood of winning at craps?


Simulation Result
Simulate 1,000 games to estimate this probability and visualize the outcomes.

```{r}
library(ggplot2)

set.seed(123)

simulate_craps_game <- function() {
  # Roll the dice 
  initial_roll <- sum(sample(1:6, 2, replace = TRUE))
  
  # Immediate win or loss
  if (initial_roll == 7 || initial_roll == 11) {
    return(TRUE)  
  } else if (initial_roll == 2 || initial_roll == 3 || initial_roll == 12) {
    return(FALSE) 
  }
  
  # Continue rolling
  point <- initial_roll
  repeat {
    new_roll <- sum(sample(1:6, 2, replace = TRUE))
    if (new_roll == point) {
      return(TRUE)  
    } else if (new_roll == 7) {
      return(FALSE) 
    }
  }
}

summarize_craps_game <- function(results) {
  total_games <- length(results)
  total_wins <- sum(results)
  win_rate <- total_wins / total_games
  
  data.frame(
    Total_Games = total_games,
    Wins = total_wins,
    Losses = total_games - total_wins,
    Win_Rate = win_rate
  )
}


run_craps_simulation <- function(N) {
  results <- replicate(N, simulate_craps_game())
  summarize_craps_game(results)
}

# Run simulation
num_games <- 1000
simulation_results <- replicate(num_games, simulate_craps_game())


summary <- summarize_craps_game(simulation_results)
print(summary)


```

Visualization of Wins and Losses

```{r}

win_loss_df <- data.frame(
  Outcome = factor(simulation_results, levels = c(TRUE, FALSE), labels = c("Win", "Loss"))
)

# Plot outcomes
ggplot(win_loss_df, aes(x = Outcome)) +
  geom_bar(fill = "pink") +
  labs(title = "Craps Game Simulation Results",
       x = "Outcome",
       y = "Count") +
  theme_minimal()

```

Simulation Variability
Assess variability by repeating the simulation multiple times and examining the distribution of win rates.

```{r}
# Repeat the simulation 50 times and calculate win rates
set.seed(123)
num_repeats <- 50
win_rates <- replicate(num_repeats, {
  results <- replicate(num_games, simulate_craps_game())
  sum(results) / num_games
})

print(summary(win_rates))

```

Variability Visualization

```{r}
# Plot distribution 
ggplot(data.frame(Win_Rate = win_rates), aes(x = Win_Rate)) +
  geom_histogram(binwidth = 0.01, fill = "lightgreen", color = "black") +
  labs(title = "Simulation Variability: Distribution of Win Rates",
       x = "Win Rate",
       y = "Frequency") +
  theme_minimal()

```